Thorough example

### 2021-01-12 inst/gitbook/04_make.events.Rmd
events and thorough example INIT (working-ish examples)

```{r}
## Extinction of any tips with trait < 1 at time 4
trait_extinction <- make.events(
                      target = "taxa",
                      condition = time.condition(4),
                      modification = trait.extinction(1))

@@

```{r}
## Simulation parameters
stop.rule <- list(max.time = 4)

@@

```{r}
## Simulation parameters
stop.rule <- list(max.time = 6)
traits <- make.traits()

@@

## Run the simulations
set.seed(1)
no_change <- dads(bd.params = bd.params,
                  stop.rule = stop.rule,
                  traits = traits)
set.seed(1)
process_change <- dads(bd.params = bd.params,
                       stop.rule = stop.rule,
                       traits = traits,
                       events = events)
## Plot the results
par(mfrow = c(1,2))
plot(no_change, ylim = c(-5, 8))
plot(process_change, ylim = c(-5, 8))
```

@@

```{r}
## Set the parameters
stop.rule <- list(max.taxa = 100)

@@

## Run the simulations
set.seed(8)
no_event <- dads(bd.params = bd.params,
                 stop.rule = stop.rule,
                 traits    = traits)
set.seed(8)
change_correlation <- dads(bd.params = bd.params,
                           stop.rule = stop.rule,
                           traits    = traits,
                           events    = events)
## Visual testing
par(mfrow = c(1,2))
plot(no_event, trait = 2)
plot(change_correlation, trait = 2)
# plot(no_event, trait = c(1:2))
# plot(change_correlation, trait = c(1:2), use.3D = TRUE)
```

@@

```{r}
## Parameters
stop.rule <- list(max.taxa = 100)
modifiers <- make.modifiers()
traits <- make.traits()

>>>>

## Extinction of any tips with trait < 1 at time 4
trait_extinction <- make.events(
                      target = "taxa",
                      condition = time.condition(4),
                      modification = trait.extinction(1))

@@

```{r}
## Simulation parameters
stop.rule <- list(max.time = 4)
bd.params <- list(extinction = 0, speciation = 1)

@@

```{r}
## Simulation parameters
bd.params <- list(extinction = 0, speciation = 1)
stop.rule <- list(max.time = 6)
traits    <- make.traits()

@@

## Run the simulations
set.seed(1)
no_change <- dads(bd.params = bd.params,
                  stop.rule = stop.rule,
                  traits    = traits)
set.seed(1)
process_change <- dads(bd.params = bd.params,
                       stop.rule = stop.rule,
                       traits    = traits,
                       events    = change_process)
## Plot the results
par(mfrow = c(1,2))
plot(no_change, ylim = c(-7, 7))
plot(process_change, ylim = c(-7, 7))
```

@@

```{r}
## Set the parameters
stop.rule <- list(max.taxa = 100)
bd.params <- list(extinction = 0, speciation = 1)

@@

## Run the simulations
set.seed(8)
no_event <- dads(bd.params = bd.params,
                 stop.rule = stop.rule,
                 traits    = traits)
set.seed(8)
change_correlation <- dads(bd.params = bd.params,
                           stop.rule = stop.rule,
                           traits    = traits,
                           events    = change_correlation)
## Visual testing
par(mfrow = c(1,2))
plot(no_event, trait = 2)
plot(change_correlation, trait = 2)
# plot(no_event, trait = c(1:2))
# plot(change_correlation, trait = c(1:2), use.3D = TRUE)
```

@@

```{r}
## Parameters
bd.params <- list(extinction = 0, speciation = 1)
stop.rule <- list(max.taxa = 100)
modifiers <- make.modifiers()
traits <- make.traits()

### 2021-01-12 inst/gitbook/05_thorough_example.Rmd
events and thorough example INIT (working-ish examples)

```{r}
## Running a birth death tree 
results <- dads(bd.params = bd_params,
                stop.rule = stop_rule,
                null.error = 100) # This option will try the requested options up until a 100 times

@@

```{r, eval = FALSE}
## Visualise the 2D trait (uncorrelated OU.process)
plot(two_traits, trait = 2, use.3D = TRUE)
```

@@

```{r}
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                null.error = 100)

@@

@@

```{r}
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation,
                null.error = 100)

@@

```{r}
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation,
                events     = events_list,
                null.error = 100)

@@

@@

```{r}
## Adding the selective event
events_list <- make.events(event.name   = "Selection",
                           add          = events_list,
                           target       = "taxa",
                           condition    = time.condition(4),
                           modification = trait.extinction(0, condition = `<`, trait = 2))
```

```{r}
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation,
                events     = events_list,
                null.error = 100)

@@

```{r}
## The new trait for the founding event
new_traits <- make.traits(process = c(BM.process, BM.process), n = c(1, 2),
                          trait.names = c("Distance", "Variables"))

@@

```{r}
## The selective event
events_list <- make.events(event.name   = "Founding", 
                           add          = events_list,
                           target       = "founding",
                           condition    = trait.condition(3),
                           modification = founding.event(traits    = new_traits,
                                                         events    = mass_extinction,
                                                         bd.params = list(
                                                            speciation = 2,
                                                            extinction = 0)),
                           additional.args = list(prefix = "found_"))
```

```{r}
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation,
                events     = events_list,
                null.error = 100)

>>>>

```{r}
set.seed(0) # 123 also works
## Running a birth death tree 
results <- dads(bd.params = bd_params,
                stop.rule = stop_rule)

@@

```{r}
## Visualise the 2D trait (uncorrelated OU.process)
plot(two_traits, trait = 2, use.3D = TRUE)
```

@@

```{r}
set.seed(0)
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits)

@@

```{r}
## Visualising the tree in 3D
plot(results, trait = c(2,3), use.3D = TRUE)
```

@@

```{r}
set.seed(42)
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation)

@@

```{r}
set.seed(8)
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation,
                events     = events_list)

@@

```{r, eval = FALSE}
## Visualising the tree in 3D
plot(results, trait = c(2,3), use.3D = TRUE)
```

@@

# BUGGED FROM HERE

```{r, eval = FALSE}
## Adding the selective event
events_list <- make.events(event.name   = "Selection",
                           add          = events_list,
                           target       = "taxa",
                           condition    = time.condition(4),
                           modification = trait.extinction(x = 0, condition = `<`, trait = 2))
```
Problem with `modification` argument here

```{r, eval = FALSE}
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation,
                events     = events_list)

@@

```{r, eval = FALSE}
## The new trait for the founding event
new_traits <- make.traits(process = c(BM.process, BM.process), n = c(1, 2),
                          trait.names = c("Distance", "Variables"))

@@

```{r, eval = FALSE}
## The selective event
events_list <- make.events(event.name   = "Founding", 
                           add          = events_list,
                           target       = "founding",
                           condition    = trait.condition(3),
                           modification = founding.event(traits    = new_traits,
                                                         events    = mass_extinction,
                                                         bd.params = list(
                                                            speciation = 2,
                                                            extinction = 0)),
                           additional.args = list(prefix = "found_"))
```

```{r, eval = FALSE}
## Running a birth death tree 
results <- dads(bd.params  = bd_params,
                stop.rule  = stop_rule,
                traits     = two_traits,
                modifiers  = distance.speciation,
                events     = events_list,
                null.error = 100)
